Functional Enrichment Tests: Intro and methods comparison

### 2023-07-14 DRAFT_Funct_Enrich.Rmd
added reticulate package for knitting. knit.
formatting updates

```{r setup, include=FALSE}
library(tidyverse)
```

@@

# Considerations for a Rigourous Analysis

@@

# Getting to Enrichment Analysis

Once the challenge of annotating data has been met, the next step is determining the focus of your functional analysis. In some cases, you will use the complete dataset, but in other cases you may be interested in a subset of interest. There are numerous approaches that can be used to achieve this, many with excellent tutorials available online. These include:

@@

-   The Gene Ontology (Thea)
-   Annotation and filtration decisions (Sam) - include key terms
-   Overrepresentation vs Enrichment (Thea)
-   Explanation of statistics (Sam) - include key terms

@@

## Annotation and filtration decisions

## Overrepresentation vs Enrichment

@@

## Explanation of Statistics

@@

# A primer on the statistics of functional enrichment

@@

## Fisher's Exact Test

@@

## Mann Whitney U Test

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(reticulate)
```

@@

## Considerations for a Rigourous Analysis

@@

## Getting to Enrichment Analysis: Annotation and Filtration Decisions

Once the challenge of annotating data has been met, the next step is determining the focus of your functional analysis. In some cases, you will use the complete dataset, but in other cases you may be interested in a subset of interest. There are numerous approaches that can be used to achieve this, many with excellent tutorials available online. Some commonly used approaches include:

@@

@@

## Overrepresentation vs Enrichment Approaches

@@

@@

## A Primer on the Statistics of Functional Enrichment

@@

### Fisher's Exact Test

@@

### Mann Whitney U Test
